Article Title

### 2019-08-25 text/index.Rmd
Make tables conform to conventions
Set up proper citations

---
title: "This is the title"
author: "The Pickles"
date: "Febcember 32nd 3023"
language: en-US
site: "bookdown::bookdown_site"
output:
  bookdown::pdf_book:
    keep_tex: true
    keep_md: true
    includes:
      in_header:
        preamble.tex
documentclass: book
---

@@

>>>>

---
title: "Article Title"
runtitle: "Short Title"
documentclass: frontiersSCNS  # or frontiersHLTH, or frontiersFPHY
author:
  - name: First Author
    affiliation: '1'
    etal: LASTNAME # First author's last name. 
  - name: Co-Author
    affiliation: '2'
  - name: Co-Author
    affiliation: '1,3'
    email: email@uni.edu # Indicates corresponding Author
    institution: Laboratory X, Institute X, Department X, Organization X
    street: Street X
    city: City X
    state: State XX # only USA, Australia, Canada
    zip: Zip Code X
    country: Country X
affiliation:
  - id: '1'
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
  - id: '2' 
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
  - id: '3' 
    department: Department X
    institution: Institution X
    city: City X
    state: State XX # only USA, Australia, Canada
    country: Country X
date: "Febcember 32nd 3023"
language: en-US
site: "bookdown::bookdown_site"
csl: frontiers.csl
bibliography: test.bib
link-citations: true
output:
  bookdown::pdf_book:
    keep_tex: true
    keep_md: true
    base_format: rticles::frontiers_article
    citation_package: natbib
    includes:
      in_header:
        preamble.tex
---

@@

```{r helper-functions}
format_genome <- function(genomes) {
  return(unlist(lapply(strsplit(genomes, "\\."), function(x) { 
    if(length(x) > 1) {
      paste0("\\textit{",gsub("_", " ",x[1]),"} ", paste(x[2:length(x)], collapse="."))
    } else {
      paste0("\\textit{",gsub("_", " ",x[1]),"} ")
    }
  }))
  )
}
```

\begin{abstract}

Abstract length and content varies depending on article type. Refer to 
\url{http://www.frontiersin.org/about/AuthorGuidelines} for abstract requirement
and length according to article type.

%All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\tiny
 \keyFont{ \section{Keywords:} Text Text Text Text Text Text Text Text }

\end{abstract}
